\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-14 doc/sw-cfhtls.tex

The \rf and the \af searches are the only searches that make use of a
lens finding algorithm and that have been run on the entire \cfhtls
imaging dataset.  Thus, we considered these to be our reference sample of known
lenses from robotic searches. For the purposes of transparency and to
help with the training, the volunteers participating in \sw-\cfhtls lens
search were made aware of these two known lens samples. Images
containing the systems from the \rf and the \af samples were labelled as
``known lens candidates'' in the \sw discussion forum,
\Talk,\footnote{\texttt{http://talk.spacewarps.org/}} where volunteers have the
opportunity to discuss their findings with fellow volunteers and the
science team. In this paper, we refer to the sample of 330 \rf and 108
\af lens candidates as the sample of ``known lens candidates'' and the
sample of confirmed (or most promising) 33 \rf and 26 \af as the sample
of ``known lenses''. Note that the ``known lens'' sample is a subset of
the ``known lens candidates'' sample. Note that the lens candidates in found in the other papers listed above were not included in our known lens candidate list and were not flagged to volunteers in \Talk. However, we did remove candidates in all the papers listed above when compiling the list of new lens candidates discovered in \sw described in \Sref{sec:results:newcand}.

@@

The discovery of many new lens candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time.  They
have found lens candidates which the algorithms failed to discover.
Upcoming and planned wide-field imaging surveys such as the DES, HSC and
LSST will produce formidable amounts of data.  Blind lens searches as
described here will be impractical with these very large surveys. However,
it should be possible to conduct a blind search on a sub-area of a large survey in
order to assess the performance of either the algorithms or the
volunteers, the results of which can be extrapolated to the entire survey.  As
demonstrated in this paper, any one approach for finding lenses from the
entire survey data may not be sufficiently complete. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening might be a good strategy for finding lenses in these
large imaging surveys.

>>>>

The \rf and the \af searches are the only searches that make use of a
lens finding algorithm and that have been run on the entire \cfhtls
imaging dataset.  Thus, we considered these to be our reference sample of known
lenses from robotic searches. For the purposes of transparency and to
help with the training, the volunteers participating in \sw-\cfhtls lens
search were made aware of these two known lens samples. Images
containing the systems from the \rf and the \af samples were labelled as
``known lens candidates'' in the \sw discussion forum,
\Talk,\footnote{\texttt{http://talk.spacewarps.org/}} where volunteers have the
opportunity to discuss their findings with fellow volunteers and the
science team. In this paper, we refer to the sample of 330 \rf and 108
\af lens candidates as the sample of ``known lens candidates'' and the
sample of confirmed (or most promising) 33 \rf and 26 \af as the sample
of ``known lenses''. Note that the ``known lens'' sample is a subset of
the ``known lens candidates'' sample. Also, note that the lens
candidates from the other papers listed above were not included in our
reference ``known'' sample and were not labelled as such in \Talk.
However, we did exclude these candidates when compiling the list of new
\sw lens candidates, as described in \Sref{sec:results:newcand}.

@@

The discovery of many new lens candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time.  They
have found lens candidates which the algorithms failed to discover.
Upcoming and planned wide-field imaging surveys such as the DES, HSC and
LSST will produce formidable amounts of data.  Blind lens searches as
described here will be impractical with these very large surveys. However,
it should be possible to conduct a blind search on a sub-area of a large survey in
order to assess the performance of either the algorithms or the
volunteers, the results of which can be extrapolated to the entire survey.  As
demonstrated in this paper, any one approach for finding lenses from the
entire survey data may not be sufficiently complete and pure. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening might be a good strategy for finding lenses in these
large imaging surveys.
